Reviewer comments from PeerJ

### 2015-02-02 PeerJComments.tex
PeerJ Reviewer comments
Comments in response to points from reviewer 1 and reviewer 2

4) It would be helpful to include Fig. S1 in the main text of the paper and to label the two sequenced regions (Region 1 and 2) in the figure itself (not just in the caption). \\
\lev{Okay can do this}.

5) Fig. S2. Annotate this figure to show the size (bp) of each band in the 1 kb ladder. The caption should also define the abbreviations used in the labels. \\
\lev{this will be too much. I can label the brightest band (1kb) and the top and bottom bands}.

@@

7) Line 118. Figure S1 should be cited here, not Table S1. \\
\lev{Okay can fix}.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

3) In the Results section, some titles like “Genotyping”, “Sequencing” or “Phenotyping” are too vague, and sound more like Materials and Methods than to Results. They should be modified in order to highlight what question is addressed.
Paragraph “Neighbor joining trees… insertion”” on lines 235-239 should be moved to the section “Evidence of introgression”.\\

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

4) It would be helpful to include Fig. S1 in the main text of the paper and to label the two sequenced regions (Region 1 and 2) in the figure itself (not just in the caption). \\
\lev{Okay can do this}

5) Fig. S2. Annotate this figure to show the size (bp) of each band in the 1 kb ladder. The caption should also define the abbreviations used in the labels. \\
\lev{this will be too much. I can label the brightest band (1kb) and the top and bottom bands}

@@

7) Line 118. Figure S1 should be cited here, not Table S1. \\
\lev{Okay can fix}

@@

\lev{yes SNPs within 5KB window are a haplotype. I don't know about the diploid/phasing stuff. Yes to maize assignment. Point of figure is that low assignment to maize in populations with high frequency of Hopscotch. Am plotting the assigment value across a region of chromosome 1. I showed a region and not entire chromosome to be able to highlight the position of tb1 and so that you can see the difference in assignment values.}

@@

\lev{No idea off the top of my head. Good point, can look up and mention}

@@

\lev{Okay can mention}

@@

\lev{will check}

@@

\lev{Okay. I am not sure that we have significance values for these.}

@@

\lev{Okay reword.}

@@

\lev{Do you guys want to do this?}

@@

\lev{I have no strong feelings about this.}

@@

\lev{Okay we can maybe take these statements out? It would seem that none of the reviewers have ever been happy with what we have had to say with respect to mex vs parv, or unequal sampling. we have discussed why sampling is unequal and why there was no phenotyping for mex.}

@@

\lev{Okay. What do you guys think of this? I don't think we have tests of significance for tajd}

@@

\lev{I don't think this is necessary. Again, everyone has seemed to want something different in the intro. Last person wanted more maize/shade avoidance/tb1. Perhaps we can add a couple of sentences in about mex vs parv or the population stuff. I would like to not have to rewrite the entire intro again.}

@@

\lev{Okay I can check to make sure citations and data stuff from tanja are clear}

3) In the Results section, some titles like “Genotyping”, “Sequencing” or “Phenotyping” are too vague, and sound more like Materials and Methods than to Results. They should be modified in order to highlight what question is addressed.
Paragraph “Neighbor joining trees… insertion”” on lines 235-239 should be moved to the section “Evidence of introgression”.\\
 \lev{I like our sections...}

@@

\lev{Simply put it is what we had available at the time. There was no specific choosing or decision about number of individuals per accession}

@@

\lev{Okay. Is there somewhere we can get all of this info.? I don't believe I have access to the database any more}

@@

\lev{Why what? Why two products? or why did we do it that way? I think it is clearly stated that we can test for presence/absence/hets and pcr bias with sometimes a large fragment being difficult to amplify. The location of the primers is all shown in the cartoon figure and stated in the text. two primers outside of LTR one primer within.}

@@

\lev{What? It is in the LTR!!!! Gah! That's the whole point!}

@@

\lev{Okay can do this. maybe will clear up their misunderstanding detailed above}

@@

\lev{I can relabel or clarify in the figure legend. I don't think that redoing a gel is possible at this point.}

@@

\lev{Redoing gel not possible at this point}

@@

\lev{I think that we did initially to check. But all of the products match the appropriate and expected size. The only issue we had was suddenly the different size with the Pif, which we did check with sequencing.}

@@

\lev{My guess is that we can look this up on WorldClim if you guys think it is necessary. My guess is that microorganisms were not included in analysis of soil characteristics, that it was things like what compounds are in soil, etc.}

@@

\lev{i will check this but i believe mexicana not included because we didn't discuss them with respect to the high frequency stuff. I do not have arcgis any more and would prefer to not completely redo this figure. I am happy to put names on pops though. I don't understand comments about 'left hand side' stuff. Yes, some of the populations are close together when you are that zoomed out on a map. There is no way to have them not all coming from the same place in some cases unless the map was so gigantic to take up an entire page.}

@@

\lev{We can relabel but not redo gels at this point}

@@

\lev{Sure greenhouse is different than outside, but we can't control for variation outside whereas we can in a greenhouse. I don't understand their point. Greenhouse is best we could do here since they wouldn't all fit in a growth chamber.}
